%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$
    {\underline{oguntade.site}} $|$
    {\underline{linkedin.com/in/aj-oguntade}} $|$
    Edmonton, AB
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science}{Expected Spring 2029}
    \resumeSubheading
      {Harry Ainlay High School}{Edmonton, AB}
      {High School Diploma}{Summer 2025}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Personal Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Transit Monkey} $|$ \emph{Flutter, Golang, SQLite}}{2024}
      \resumeItemListStart
        \resumeItem{Architected a high-performance backend API in Golang to minimize latency during trip planning.}
        \resumeItem{Implemented a CLI database builder to convert GTFS zip files into SQLite databases, enabling deployment on any server.}
        \resumeItem{Implemented client-side downloading and processing of GTFS zip files for offline use.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{composite-highlighting.nvim} $|$ \emph{Lua, Neovim, Treesitter}}{2025}
      \resumeItemListStart
        \resumeItem{Developed and published an open-source Neovim plugin enabling simultaneous Treesitter-based syntax highlighting for two languages within a single file.}
        \resumeItem{Implemented a custom Treesitter injection directive with dynamic inner-language detection based on filename conventions (e.g., \texttt{page.html.tmpl}).}
        \resumeItem{Designed a configurable API supporting multiple template engines (Go templates, Jinja2, ERuby) with sensible defaults and fallback logic.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{Function} $|$ \emph{Flutter, Firebase, Dart}}{2024}
      \resumeItemListStart
        \resumeItem{Developed a social discovery feature enabling users to track real-time events hosted by people in their network.}
        \resumeItem{Built full-stack features including secure user authentication, profile management, and a comprehensive search algorithm.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Created visually compelling posters and advertisements for Instagram, enhancing brand visibility and engagement.}
        \resumeItem{Managed up to 5 projects simultaneously, meeting tight deadlines and ensuring high-quality deliverables.}
        \resumeItem{Collaborated with the Marketing Team to develop and execute promotional strategies and campaigns.}
        \resumeItem{Designed social media graphics ensuring consistency with brand guidelines.}
        \resumeItem{Conducted market research to stay updated on current design trends and competitor activities.}
      \resumeItemListEnd

    \resumeSubheading
      {School Library Assistant}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Organized and cataloged books and resources, ensuring easy access and efficient retrieval for students and staff.}
        \resumeItem{Assisted students and teachers with technical difficulties and research obstacles, providing prompt resolutions.}
        \resumeItem{Managed the library's help desk, responding to requests for assistance with research, technology, and resources.}
        \resumeItem{Provided technical support for library computers and digital devices, assisting users with troubleshooting.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Backend \& Database}{: Firebase, Golang, SQLite, Data Processing, Server Management, Linux} \\
     \textbf{Mobile Development}{: Flutter/Dart, React Native/TypeScript} \\
     \textbf{Web Development}{: Server-Side Rendering (SSR), Golang, HTMX, Tailwind CSS, HTML/CSS} \\
     \textbf{Languages}{: C/C++, C\#, Python, JavaScript} \\
     \textbf{Design}{: App/Website Graphics, Brand Consistency, Marketing Material Design} \\
     \textbf{Soft Skills}{: Versatility, Optimism, Problem Solving \& Troubleshooting, Communication}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
