%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$ 
    {\underline{oguntade.site}} $|$ 
    {\underline{linkedin.com/in/aj-oguntade}} $|$ 
    Edmonton, AB
\end{center}

%-----------SKILLS-----------
\section{Design \& Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Creative Software}{: Adobe Creative Suite (Photoshop, Illustrator), Figma, Canva, Inkscape} \\
     \textbf{Design Competencies}{: UI/UX Design, Brand Identity, Typography, Layout Design, Social Media Marketing} \\
     \textbf{Web/Frontend}{: HTML/CSS, Tailwind CSS, JavaScript, React Native, Flutter (UI Implementation)} \\
     \textbf{Technical Tools}{: Linux (Arch/Hyprland), Neovim, Git/GitHub, C/C++, Python}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Design Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Conceptualized and produced visually compelling posters and advertisements for Instagram, increasing organic engagement by translating brand values into modern aesthetics.}
        \resumeItem{Maintained strict brand consistency across all marketing materials, ensuring high-fidelity deliverables for diverse digital campaigns.}
        \resumeItem{Managed a high-volume workflow of up to 5 concurrent projects, meeting tight deadlines through efficient asset management and iteration.}
        \resumeItem{Collaborated with the Marketing Team to refine visual strategy based on current design trends and competitor research.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Design \& UI Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Social Media App (Iconic)}{2024 -- 2026}
      {Lead UI/UX Designer \& Developer}{React Native, Tailwind CSS}
      \resumeItemListStart
        \resumeItem{Designed a comprehensive mobile UI focused on "Social Discovery," prioritizing intuitive navigation and real-time visual feedback for event tracking.}
        \resumeItem{Developed a cohesive design system including custom iconography, color palettes, and typography to ensure a unified brand identity across the app.}
        \resumeItem{Iterated on high-fidelity prototypes to optimize user flows for authentication and search functionality.}
      \resumeItemListEnd

    \resumeSubheading
      {Personal Branding \& Web Identity}{2025 -- 2026}
      {Designer \& Frontend Developer}{Tailwind CSS, HTMX, Go}
      \resumeItemListStart
        \resumeItem{Designed and developed a minimalist, performance-focused personal portfolio to showcase design case studies and technical projects.}
        \resumeItem{Established a consistent personal brand identity through custom typography, a curated color palette, and cohesive iconography.}
        \resumeItem{Optimized user experience by implementing responsive, accessible UI components for a seamless cross-platform viewing experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Trip Planner Interface}{2024}
      {UI Design \& Full-Stack Development}{Flutter, Dart}
      \resumeItemListStart
        \resumeItem{Designed a clean, minimalist interface for complex transit data visualization, emphasizing readability and ease of use in mobile environments.}
        \resumeItem{Built a custom design language for offline map states and data-heavy list views to maintain visual clarity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------OTHER EXPERIENCE-----------
\section{Additional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School Library Assistant}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Managed information organization and assisted users with digital tools, demonstrating strong attention to detail and communication skills.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science}{Expected Spring 2029}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
