%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$
    {\underline{oguntade.site}} $|$
    {\underline{linkedin.com/in/aj-oguntade}} $|$
    Edmonton, AB
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science, Minor in Philosophy}{Expected Spring 2029}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Personal Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Custom Minecraft Server} $|$ \emph{Server Configuration, Networking}}{2024}
      \resumeItemListStart
        \resumeItem{Built and configured a cross-platform Minecraft server allowing players on different devices (like PC and tablets) to play together seamlessly.}
        \resumeItem{Managed backend settings to ensure a smooth, lag-free experience for players.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Iconic Mobile App} $|$ \emph{React Native, TypeScript, Supabase}}{2024 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a mobile app that helps users connect and discover local events hosted by friends.}
        \resumeItem{Set up the main database and built features like secure user profiles and search tools.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Code Color-Coding Tool} $|$ \emph{Lua, Open Source}}{2025}
      \resumeItemListStart
        \resumeItem{Created and shared a free tool for a popular coding program that color-codes different programming languages at the same time.}
        \resumeItem{Designed the tool to be highly customizable so other programmers can easily read and organize their work.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{Offline Trip Planner} $|$ \emph{Mobile App Development}}{2024}
      \resumeItemListStart
        \resumeItem{Built an app that helps users plan travel routes and view maps even when they don't have internet access.}
        \resumeItem{Programmed the backend system to process travel data quickly so the app runs smoothly without long loading times.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Designed fun and engaging posters and social media posts to grab people's attention.}
        \resumeItem{Worked on multiple creative projects at the same time, making sure everything was finished on schedule.}
        \resumeItem{Collaborated with a team to brainstorm new ideas for campaigns and learning materials.}
      \resumeItemListEnd

    \resumeSubheading
      {School Library Assistant}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Helped students and teachers troubleshoot computer issues and learn how to use new digital tools.}
        \resumeItem{Ran the library help desk, patiently answering questions and explaining how to find information.}
        \resumeItem{Organized educational resources and books so students could easily find what they needed for their projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming \& Tech}{: Python, JavaScript, React Native, Mobile App Building, Game Server Setup, Web Development, Linux} \\
     \textbf{Creative \& Design}{: App/Website Graphics, Making Learning Materials, Brand Consistency} \\
     \textbf{Teaching \& Soft Skills}{: Explaining Technical Concepts Clearly, Patient Troubleshooting, Mentoring, Problem Solving, Optimism}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
