%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$
    {\underline{oguntade.site}} $|$
    {\underline{linkedin.com/in/aj-oguntade}} $|$
    Edmonton, AB
\end{center}

%-----------OBJECTIVE-----------
\section{Objective}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Energetic and dependable individual seeking a outdoor work, summer camp counselor, or
      general handyperson role. Proven ability to manage multiple responsibilities simultaneously,
      collaborate with diverse teams, and support others in fast-paced environments. Passionate
      about working outdoors, fostering a positive atmosphere, and contributing meaningfully to
      any team.
    }}
  \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science}{Expected Spring 2029}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Managed up to 5 concurrent projects simultaneously, consistently meeting tight deadlines while maintaining high-quality outputs --- demonstrating strong time management and composure under pressure.}
        \resumeItem{Collaborated closely with a Marketing Team to plan and execute campaigns, contributing ideas and adapting based on group feedback.}
        \resumeItem{Created engaging visual materials to promote events and initiatives, increasing audience reach and community participation.}
        \resumeItem{Conducted ongoing research to stay informed on trends, developing a habit of learning and adapting quickly to new information.}
      \resumeItemListEnd

    \resumeSubheading
      {School Library Assistant}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Supported students and staff daily with research, technology, and resource needs --- consistently delivering patient, friendly, and effective assistance.}
        \resumeItem{Organized and maintained a large inventory of books and resources, ensuring everything remained orderly, accessible, and easy to navigate.}
        \resumeItem{Managed a help desk for a diverse school community, developing strong communication and problem-solving skills across varied requests.}
        \resumeItem{Provided hands-on troubleshooting support for computers and digital devices, resolving issues calmly and efficiently.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACTIVITIES & CONTRIBUTIONS-----------
\section{Activities \& Contributions}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Open-Source Software Contributor} $|$ \emph{Independent}}{2025}
      \resumeItemListStart
        \resumeItem{Independently designed, built, and published a tool used by others --- demonstrating initiative, follow-through, and the ability to work without supervision toward a meaningful goal.}
        \resumeItem{Wrote clear documentation and gathered user feedback, reflecting strong communication habits and attention to others' needs.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{App \& Software Development} $|$ \emph{Self-Directed Projects}}{2024}
      \resumeItemListStart
        \resumeItem{Planned and executed multi-phase projects from concept to completion on personal timelines, building strong habits around goal-setting, iteration, and accountability.}
        \resumeItem{Collaborated with peers on development projects, taking shared ownership of outcomes and navigating disagreements constructively.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------SKILLS-----------
\section{Skills \& Strengths}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Interpersonal}{: Working with youth and diverse groups, active listening, conflict de-escalation, mentorship} \\
     \textbf{Leadership \& Organization}{: Task prioritization, event coordination, inventory management, team support} \\
     \textbf{Practical \& Handy}{: General maintenance awareness, tool familiarity, setup and takedown of equipment, basic repairs} \\
     \textbf{Creative}{: Activity and program design, promotional material creation, visual communication} \\
     \textbf{Soft Skills}{: Reliability, adaptability, positive attitude, initiative, calm under pressure, teamwork}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
