%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$
    {\underline{oguntade.site}} $|$
    {\underline{linkedin.com/in/aj-oguntade}} $|$
    Edmonton, AB
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science, Minor in Philosophy}{Expected Spring 2029}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {School Library Assistant \& Tech Support}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Managed the library's IT help desk, delivering direct customer service and technical support to students and staff.}
        \resumeItem{Diagnosed and resolved hardware and software issues on library computers and digital devices promptly.}
        \resumeItem{Assisted users with research obstacles and database navigation, translating technical concepts into accessible language.}
        \resumeItem{Organized and cataloged resources, ensuring efficient retrieval and maintaining a welcoming environment for patrons.}
      \resumeItemListEnd

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Collaborated closely with the Marketing Team to determine client needs and execute visual promotional strategies.}
        \resumeItem{Managed up to 5 simultaneous projects, effectively prioritizing tasks to meet tight deadlines without sacrificing quality.}
        \resumeItem{Delivered high-quality customer experiences by ensuring strict brand consistency across all public-facing materials.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS & TECHNICAL EXPERIENCE-----------
\section{Technical Projects \& Hardware Experience}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Hardware Troubleshooting \& OS Setup} $|$ \emph{Device Configuration, Network Streaming}}{2025 -- 2026}
      \resumeItemListStart
        \resumeItem{Installed and configured a variety of operating systems (Linux, Windows, ChromeOS) on diverse hardware, successfully diagnosing and resolving complex driver and compatibility issues.}
        \resumeItem{Managed physical storage partitions and system configurations to optimize long-term device performance.}
        \resumeItem{Configured low-latency remote desktop streaming environments across multiple devices to ensure seamless connectivity and user experience.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Server Administration} $|$ \emph{Networking, Server Plugins}}{2026}
      \resumeItemListStart
        \resumeItem{Configured and deployed remote multiplayer gaming servers, managing client-side optimizations and cross-play bridging plugins.}
        \resumeItem{Troubleshot network latency, server whitelisting, and backend configurations to ensure seamless user connectivity.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Iconic (Mobile Application)} $|$ \emph{React Native, TypeScript, Supabase}}{2026}
      \resumeItemListStart
        \resumeItem{Developing a full-stack social application with a strong focus on intuitive user interface design and accessibility.}
        \resumeItem{Actively debugging client-side features and authentication flows based on end-user usability requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical Support}{: Hardware Troubleshooting, OS Installation, Network Configuration, Help Desk Operations} \\
     \textbf{Operating Systems}{: A variety of operating systems (Linux, Windows, ChromeOS, macOS), Terminal/CLI} \\
     \textbf{Customer Service}{: Client Communication, Problem Solving, Active Listening, Task Prioritization} \\
     \textbf{Software \& Development}{: React Native, TypeScript, Neovim, Golang, Firebase, Supabase}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
