%-------------------------
% Resume in LaTeX
% Author: AJ Oguntade
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape AJ Oguntade} \\ \vspace{4pt}
    \small (587) 778-1290 $|$
    Edmonton, AB
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {School Library Assistant}{September 2022 -- January 2023}
      {Harry Ainlay High School}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Served as a first point of contact at the help desk, assisting students and staff with research, technology, and resource requests in a friendly and efficient manner.}
        \resumeItem{Resolved technical difficulties and troubleshooting issues for library computers and devices, maintaining a calm and helpful demeanor under pressure.}
        \resumeItem{Organized and maintained a large inventory of books and resources, ensuring accurate cataloging and easy retrieval for patrons.}
        \resumeItem{Collaborated daily with teachers and staff to fulfill resource requests and support a smooth, welcoming library environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Graphic Design Intern}{July 2023 -- August 2023}
      {Canadian Imperial Advantage}{Edmonton, AB}
      \resumeItemListStart
        \resumeItem{Worked closely with the Marketing Team to understand client needs and deliver on-brand promotional materials on tight timelines.}
        \resumeItem{Managed up to 5 concurrent projects, consistently meeting deadlines while maintaining high quality and attention to detail.}
        \resumeItem{Communicated regularly with team members to align on expectations and incorporate feedback throughout the design process.}
        \resumeItem{Conducted market research to adapt work to current trends, demonstrating initiative and a willingness to learn.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Science in Computer Science}{Expected Spring 2029}
    \resumeSubheading
      {Harry Ainlay High School}{Edmonton, AB}
      {High School Diploma}{Summer 2025}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Customer Service}{: Front-facing communication, conflict resolution, active listening, patron assistance} \\
     \textbf{Organization}{: Inventory management, cataloging, multi-tasking, attention to detail} \\
     \textbf{Technology}{: Computer troubleshooting, Microsoft Office, Google Workspace, basic technical support} \\
     \textbf{Teamwork}{: Cross-functional collaboration, feedback incorporation, deadline management} \\
     \textbf{Soft Skills}{: Reliability, adaptability, positive attitude, problem solving, clear written and verbal communication}
    }}
 \end{itemize}

%-----------ADDITIONAL-----------
\section{Additional}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Independent Software Projects} $|$ \emph{Flutter, Golang, Lua}}{2024 -- 2025}
      \resumeItemListStart
        \resumeItem{Designed and shipped multiple personal software projects, demonstrating self-motivation, follow-through, and the ability to learn new tools independently.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
